---
title: "IFN704"
author: "Paramita Parinyanupap"
date: "29/08/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Data
Load necessary Library and read the data in
```{r}
library(haven)
library(dplyr)
library(ggplot2)
library(foreign)
library(nnet)
library(reshape2)
library(Hmisc)
library(MASS)
library(stringr)
library(rcompanion)

data17 <- read_spss("spss1/Combined q170c.sav")
data17 <- data17 %>% rename_all(~stringr::str_replace(., "q", ""))
data17a <- data17[c("gh9h", "wsce", "bncall", "jbhruc", "hgage1", "edhigh1", "hgsex1", "gh1", "mrcurr")]

colnames(data17a)
df2 <- rename(data17a, c(
    "happiness" = "gh9h",
    "wage" = "wsce",
    "government_allowances" = "bncall",
    "hour" ="jbhruc",
    "age" = "hgage1",
    "education" ="edhigh1",
    "gender" ="hgsex1",
    "health" ="gh1",
    "marital_status" ="mrcurr")
)

colnames(df2)
dim(df2) 
# check percentage of missing value
colMeans(is.na(df2))


# convert data type
library(rccdates)
df2 <- within(df2, {
  gender <- factor(gender, levels = 1:2, labels = c("male", "female"))
  education <- factor(education, levels = c(9, 8, 5, 4, 3, 2, 1), labels = c("Year 11 or below", "Year 12", "Cert III or IV", "Adv Diploma, diploma", "Bachelor or honours","Grad diploma, grad certificate", "Postgrad - masters or doctorate"))
  happiness <- factor(happiness, levels = 6:1, labels = c("None of the time", "A little of the time", "Some of the time", "A good bit of the time", "Most of the time", "All of the time"))
  health <- factor(health, level = 5:1, labels = c("Poor", "Fair", "Good", "Very good", "Excellent"))
})


df2$marital_status <- factor(df2$marital_status, levels = c(1,2,3,4,5,6), labels = c("Married", "Defacto", "Seperated", "Divorced", "Widowed", "Single"))

df2 <- na.omit(df2)

# filter age within 18 and 65 -> labour force
df2 <-df2 %>%
  filter(age > 18 & age < 65)


dim(df2)
summary(df2)
```


## Data Description
```{r}
summary(df2$education)
```

I choose the variables from HILDA dataset, which includes wage, government allowances (bncall), weekly work hour, age, education (edhigh1), and happiness.
The detail of variable
- wage(wsce) is currently weekly gross wages and salary, all jobs, includes estimated from net($) [weighted topcode]
- government_allowances (bncall) is the current weekly Australian Government Allowances ($)
- hour: Hours per week usually worked in all jobs
- age
- gender
    [1] Male
    [2] Female
- education (qedhigh1) is history of highest education level achieved
    [10] undetermined
    [1] Postgrad - masters or doctorate
    [2] Grad diploma, grad certificate
    [3] Bachelor or honours
    [4] Adv diploma, diploma
    [5] Cert III or IV
    [8] Year 12
    [9] Year 11 or below

- health (gh1) is self-assessed health
    [-4] refused/ not stated
    [-5] multiple response SCQ
    [-8] No SCQ
    [1] Excellent
    [2] Very good
    [3] Good
    [4] Fair
    [5] Poor

- happiness (gh9h) is A9h Mental Health: Been a happy person
  Answering in scale "Have you been a happy person?"
    [-4] refused/ not states
    [-5] multiple response SCQ
    [-8] no SCQ
    [1] All of the time
    [2] Most of the time
    [3] A good bit of the time
    [4] Some of the time
    [5] A little of the time
    [6] None of the time

- country of birth (ancob) in which country were you born?
    change the value of interest to Australian = 1 and the rest = 0
    the same value for all waves but indifferent variable for wave 1 aancob, wave 2 bancob

- employment contract - current job (jbmcnt)
    [-1] Not asked
    [-4] refused/not stated
    [1] Employed on a fixed-term contract
    [2] Employed on a casual basis
    [3] Employed on a permanent or ongoing basis
    [8] Other

- E36a total pay satisfaction (jbmssec)
- job security satisfaction (jbmssec)
- work satisfaction (jbmswrk)
- the hour of work satisfaction (jbmshrs)

- year of survey display in wave
- xwaveid = id for cross

marital status
  1	Legally married
  2	De facto
  3	Separated
  4	Divorced
  5	Widowed
  6 Never married and not de facto

## 1. Data Exploration
Continuous variable
hour, wage, government_allowances, age

Checking normal distribution
- normal
- wage is right skews

Categorical variable
- Ordinal: education, happiness
- Nominal: sex, marital status
As the hour increased, the average of people will be less happy.
As the wage increased, people tend be less happy. The reason can be the people who gain high wage work in the high stress position.
For government allowances, there is no difference between each level of happiness.


```{r}
# Boxplot
colnames(df2)
df.l <- df2[c("hour", "wage", "age", "government_allowances","happiness")]
df.m <- melt(df.l, id.var = "happiness")

p <- ggplot(data = df.m, aes(x = variable, y = value)) + geom_boxplot(aes(fill = happiness))
p + facet_wrap(~ variable, scales = "free")

```

```{r}
par(mfrow=c(2,2))
ggplot(df2, aes(x = gender, fill = happiness)) + geom_bar(position = "stack")
ggplot(df2, aes(x = education, fill = happiness)) + geom_bar(position = "stack")
ggplot(df2, aes(x = health, fill = happiness)) + geom_bar(position = "stack")
ggplot(df2, aes(x = marital_status, fill = happiness)) + geom_bar(position = "stack")
```


```{r}
library(corrplot)
library(Hmisc)
df3 <- df2[c("hour", "wage", "government_allowances")]
df3.cor <- cor(df3, method = c("spearman"))
df3.cor
corrplot(df3.cor)
```
Correlation matrix shows that there is no multicollinearity problem. However, hour and wage are almost highly correlated.


## 2. Data Partition
```{r}
ind <-sample(2, nrow(df2), replace = TRUE, prob = c(0.7, 0.3))
train <- df2[ind == 1,]
test <- df2[ind == 2,]
```


# Model

```{r}
library(MASS)
library(Hmisc)
orderlog <- polr(happiness ~ wage + government_allowances + hour + age + education + gender + health + marital_status, data = train, Hess = TRUE)
summary(orderlog)
logLik(orderlog)
```


```{r}
# p-Value Calculation
m1.coef <- data.frame(coef(summary(orderlog)))
m1.coef$pval = round((pnorm(abs(m1.coef$t.value), lower.tail = FALSE) * 2), 2)
m1.coef
```
```{r}
# export the model p-value data
library(stargazer)
stargazer(orderlog, type = "text", out = "orderlog.txt")
```

```{r}
# odd ratio
ci <- confint.default(orderlog)
exp(cbind(OR = coef(orderlog), ci))
```


# Model Performance
```{r}
# predict train
train_pred <- predict(orderlog, train)

# predict test
test_pred <- predict(orderlog, test)
```


```{r}
library(caret)
confusionMatrix(train_pred, train$happiness, positive = "pos")
```
```{r}
confusionMatrix(test_pred, test$happiness, positive = "pos")
```



Source:
https://stats.idre.ucla.edu/r/dae/ordinal-logistic-regression/

